---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# alphaN

<!-- badges: start -->
[![CRAN Version](https://www.r-pkg.org/badges/version/alphaN)](https://cran.r-project.org/package=alphaN)
[![Downloads](http://cranlogs.r-pkg.org/badges/grand-total/alphaN?color=brightgreen)](https://CRAN.R-project.org/package=alphaN)
[![Downloads](https://cranlogs.r-pkg.org/badges/alphaN?color=brightgreen)](https://CRAN.R-project.org/package=alphaN)
<!-- badges: end -->

The goal of alphaN is to help the user set their significance level as a function of the sample size. The function `alphaN` allows users to set the significance level as function of the sample size based on the evidence and the prior features they desire. The function `JABt` and `JABp` converts test statistics and $p$-values into sample size dependent Bayes factors. `JAB_plot` plots the Bayes factor as a function of the $p$-value, and `alphaN_plot` plots the alpha level as a function of sample size for a given Bayes factor.

Calculations are based on [Wulff & Taylor (2024)](https://journals.sagepub.com/doi/10.1177/14761270231214429). If you enjoy the package, please consider citing the paper.

If you’re not an R user, you may also be interested in the associated [Shiny app](https://crossvalidated.shinyapps.io/alphaN/).

## Installation

To install the latest release version from CRAN use

``` r
install.packages("alphaN")
```

You can install the development version of alphaN from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jespernwulff/alphaN")
```

## Example

Here is an example: We are planning to run a linear regression model with 1000 observations. We thus set `n = 1000`. The default `BF` is 1 meaning that we want to avoid Lindley's paradox, i.e. we just want the null and the alternative to be at least equally likely when we reject the null. 

```{r, warning=FALSE}
library(alphaN)

alpha <- alphaN(n = 1000, BF = 1)
alpha
```

Therefore, to obtain evidence of at least 1, we should set our alpha to `r round(alpha,4)`. 
