---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# alphaN

<!-- badges: start -->
<!-- badges: end -->

The goal of alphaN is to help the user set their significance level as a function of the sample size. 

## Installation

You can install the development version of alphaN from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jespernwulff/alphaN")
```

## Example

Here is an example: We are planning to run a linear regression model with 1000 observations. We thus set `n = 1000`. The default `BF` is 1 meaning that we want to avoid Lindley's paradox, i.e. we just want the null and the alternative to be at least equally likely when we reject the null. 

```{r}
library(alphaN)
alpha <- alphaN(n = 1000, BF = 1)
alpha
```

Therefore, to obtain evidence of at least 1, we should set our alpha to `r round(alpha,4)`. 


